### 2016-11-10 R/ITHIM.Rmd
Added roxygen2 to install.packages() and set compute <- TRUE

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
# install.packages(c("knitr","ggplot2","dplyr","openssl","httr", "git2r","devtools"))
library("ggplot2")
library("devtools")
library("reshape2")
library("plyr")
library("dplyr")
```

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
install.packages(c("knitr","ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("ggplot2")
library("devtools")
library("reshape2")
library("plyr")
library("dplyr")
```
